The language of generalization: Probability, vagueness, and interaction

### 2018-02-05 paper/comgen-paper.Rmd
simply fig1, modularize code to analysis script for model simulation, cache model sims

```{r rsaHelpers}
rsaHelpers <- '
var probability = function(Dist, x) {
    return Math.exp(Dist.score(x));
}
var targetUtterance = "generic";

var round = function(x){
  return Math.round(x*1000)/1000
}
var utterancePrior = Infer({model: function(){
  return uniformDraw([targetUtterance,"silence"])
}});

var thetaBins = map(round, _.range(0.01, 0.98, 0.01))
// var thetaBins = [
//    0.01, 0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
//    0.5, 0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95
 // ]
var thetaPrior = Infer({model: function(){
 return uniformDraw(thetaBins)
}});

var bins = map(round, _.range(0.01, 0.99, 0.01))

// var bins = [
  // 0.01,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,
  // 0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,0.99
// ];

var meaning = function(utt,state, theta) {
  return utt=="generic"? state > theta :
         utt=="generic is false"? state<=theta :
         utt=="silence"? true :
         utt=="some"? state>0.01:
         utt=="most"? state> 0.5:
         utt=="all"? state >= 0.99:
         true
}

var mixture = data.prior.mix[0];
var priorParams = data.prior.params[0];

var statePrior = Infer({model: function(){
  var component = flip(mixture);
  return component ?
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta(priorParams), b) + Number.EPSILON
      }, bins )
    }) :
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
      }, bins )
    })
}});
'
```

```{r rsaInterpretationModels, eval = T, cache = T}
no.utterance.model <- '
var noUtteranceInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    return { state }
 }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

fixed.threshold.model <- '
var fixedThresholdInterpreter = function(threshold) {
  Infer({model: function(){
  // var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
  var state = sample(statePrior)
  condition( state > threshold)
    return {
      state: state
  }
 // }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
 }, method: "enumerate"})}
'

uncertain.threshold.model <- '
var uncertainThresholdInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    factor( Math.log(state) )
    return {
      state: state, 
  }
  }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

```{r simulationCalls}
fixed.threshold.calls <- '
_.fromPairs(map(function(t){return [t, fixedThresholdInterpreter(t)]}, [0.1, 0.3, 0.5, 0.7, 0.9]))
'
no.utterance.call <- ' 
  noUtteranceInterpreter()
'
uncertain.threshold.call <- '
  uncertainThresholdInterpreter()
'
```

```{r simulationRuns}
priorNames <- c(
  "doesntEatPeople", #"uniformRare", 
  "isFemale", 
  "laysEggs", 
  #"eatsFood", 
  "barks",
  "carriesMalaria",
  "hasSpots"
 # "areSick"
  )
priorShapes <- list(
  isFemale =  list(params = data.frame(a = 10, b = 10), mix = 1), 
  laysEggs =  list(params = data.frame(a = 10, b = 10), mix = 0.4), 
  doesntEatPeople =  list(params = data.frame(a = 50, b = 1), mix = 1), 
  barks =  list(params = data.frame(a = 5, b = 1), mix = 0.4), 
  hasSpots =  list(params = data.frame(a = 5, b = 1), mix = 0.7), 
  carriesMalaria =  list(params = data.frame(a = 2, b = 10), mix = 0.4)
)

sims.fixed.thresholds <- data.frame()
sims.priors <- data.frame()
sims.uncertain.thresholds <- data.frame()

for (p in priorNames){

  inputData = list(prior = priorShapes[[p]])
  rs.fixed.threshold.model <- webppl(paste(rsaHelpers, fixed.threshold.model, fixed.threshold.calls, sep = '\n'), data = inputData, data_var = "data")
  rs.uncertain.threshold.model <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
  rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")

  sims.fixed.thresholds <- bind_rows(sims.fixed.thresholds,
    bind_rows(
      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.1`) %>% rename(prob = probs), 20000), threshold = 0.1) ,
      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.3`) %>% rename(prob = probs), 20000), threshold = 0.3),
      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.5`) %>% rename(prob = probs), 20000), threshold = 0.5),
      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.7`) %>% rename(prob = probs), 20000), threshold = 0.7),
      mutate(get_samples(data.frame(rs.fixed.threshold.model$`0.9`) %>% rename(prob = probs), 20000), threshold = 0.9)
    ) %>% 
      mutate(PriorShape = p)
    )

  sims.uncertain.thresholds <- bind_rows(sims.uncertain.thresholds, rs.uncertain.threshold.model %>% select(value) %>% rename(state = value) %>% mutate(PriorShape = p))
  sims.priors <- bind_rows(sims.priors, rs.prior %>% select(value) %>% rename(state = value) %>% mutate(PriorShape = p))
}
```

```{r cache = F}
fig.sims.priors <- ggplot(sims.priors, aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    ylab("Normalized probability density") +
    xlab("")+
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~., scales = 'free')+
    theme(strip.text.y = element_blank())
```

```{r cache = F}
fig.sims.fixed.thresholds <- ggplot(sims.fixed.thresholds, aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.3)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence of the feature in a category") +
    ylab("") +
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~threshold, scales = 'free')+
    theme(strip.text.y = element_blank(), axis.title.x = element_text(hjust = 1))
```

```{r cache = F}
fig.sims.uncertain.threshold <- sims.uncertain.thresholds %>% mutate(PriorShape = factor(PriorShape, 
                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria"))) %>% 
                              ggplot(., aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("") +
    ylab("") +
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~., scales = 'free')+
    theme(strip.text.y = element_blank())#element_text(angle = 0, hjust = 0))
```

```{r fig.width = 9, eval = F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,0,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")

prow <- plot_grid( p1 + theme(legend.position="none"),
           p2 + theme(legend.position="none"),
           p3 + theme(legend.position="none"),
           align = 'vh',
           labels = c("A", "B", "C"),
           hjust = -1,
           nrow = 1,
           #rel_widths = c(1.2, 3, 2)
           rel_widths = c(1.2, 3, 1.2)
           )
#prow
#legend <- get_legend(p1)

#plot_grid( prow, legend, rel_widths = c(3, .3))
```

```{r simluationEndorsementModel, eval = T, cache = T}
s1.model <- '
var interpreter = cache(function(utterance) {
  Infer({model: function(){
    var state = sample(statePrior)
    var theta = utterance == "generic" ? sample(thetaPrior) : -99
    condition(meaning(utterance, state, theta))
    return state
 }})}, 10000)

var alpha = 2

var endorser = function(featureProb){
  Infer({model: function(){
    var endorsement = sample(utterancePrior)
    var L0 = interpreter(endorsement)
    factor(alpha * L0.score(featureProb))
    return endorsement
  }})
}
// console.log(data.featureProb[0])
probability(endorser(data.featureProb[0]), "generic")
'

exampleGenerics <- c(
  "sharksDontEatPeople",
  "robinsAreFemale", 
  "robinsLayEggs", 
  "kangaroosHaveSpots",
  "dogsBark",
  "mosquitosCarryMalaria"
  )

exampleParameters <- list(
  robinsAreFemale =  list(prior = list(params = data.frame(a = 10, b = 10), mix = 1), featureProb = 0.5), 
  robinsLayEggs =  list(prior = list(params = data.frame(a = 10, b = 10), mix = 0.2), featureProb = 0.5), 
  sharksDontEatPeople =  list(prior = list(params = data.frame(a = 50, b = 1), mix = 1), featureProb = 0.8), 
  dogsBark =  list(prior = list(params = data.frame(a = 5, b = 1), mix = 0.4), featureProb = 0.9), 
  kangaroosHaveSpots =  list(prior = list(params = data.frame(a = 5, b = 1), mix = 0.7), featureProb = 0.1), 
  mosquitosCarryMalaria =  list(prior = list(params = data.frame(a = 1, b = 30), mix = 0.1), featureProb = 0.1)
)

s1.simulations <- data.frame()
for (p in exampleGenerics){

    s1.rs <- webppl(paste(rsaHelpers, s1.model, sep = "\n"), data = exampleParameters[[p]], data_var = "data")
    s1.simulations <- bind_rows(s1.simulations,
                                   data.frame(example = p, endorsement = s1.rs, featureProb = exampleParameters[[p]]["featureProb"] ))

}

```{r}
s1.simulations.relabeled <- s1.simulations %>%
  mutate(example = factor(example, 
                          levels = c("dogsBark", "kangaroosHaveSpots", "sharksDontEatPeople", "robinsLayEggs", "robinsAreFemale", "mosquitosCarryMalaria"),
                            labels = 
                            c("Dogs bark", "Kangaroos have spots", "Sharks don't eat people", "Robins lay eggs", "Robins are female", "Mosquitos carry malaria")
                            #c("Dogs", "Kangaroos", "Sharks", "Robins ", "Robins", "Mosquitos")
                          ))

# s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
#   #geom_jitter(width = 0.1, shape = 21, size = 5)+
#   #ylab("Human endorsement probability")+
#   #xlab("Frequency of target")+
#   geom_label_repel(data = s1.simulations.relabeled, 
#                    aes( label = example, fill = example),
#                        color = 'white',
#     box.padding = unit(0.0, "lines"),
#     #point.padding = unit(1e-06, "lines"),
#     segment.color = 'grey37')+
#   scale_fill_solarized()+
#   scale_x_continuous(limits = c(0, 1), 
#                      breaks = c(0, 0.5, 1))+
#   scale_y_continuous(limits = c(-0.01, 1.01), 
#                      breaks = c(0, 1),
#                      labels = c("False", "True"))+
#   coord_fixed(ratio = 1)+
#   guides(fill = F)+
#   ylab("Endorsement model prediction")+
#   xlab("Hypothesized prevalence")

s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example))+
  geom_col(color = 'black')+
  # geom_label_repel(data = s1.simulations.relabeled, 
  #                  aes( label = example, fill = example),
  #                      color = 'white',
  #   box.padding = unit(0.0, "lines"),
  #   #point.padding = unit(1e-06, "lines"),
  #   segment.color = 'grey37')+
  scale_fill_solarized()+
  scale_x_continuous(limits = c(0, 1), 
                     breaks = c(0, 1))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 1),
                     labels = c("False", "True"))+
  #coord_fixed(ratio = 1)+
  coord_flip()+
  facet_grid(example~.)+
  guides(fill = F)+
  ylab("")+xlab("Referent prevalence")+
  theme(strip.text.y = element_text(angle = 0, hjust = 0)
        #axis.title.x = element_text(hjust = 0)
        #axis.title.y = element_text(vjust = 0)
        )
  #ylab("Endorsement model prediction")+
  #xlab("Hypothesized prevalence")
```

```{r simulations, fig.cap = "Computational model behavior. A: Prior distributions over the prevalence of a feature in a category for 6 example features B: Different fixed thresholds (columns) give rise to different partial interpretations. C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors. D: Endorsement model predictions, assuming a particular referent-prevalence. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,2,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))

prow <- plot_grid( 
  add_sub(p1 + theme(legend.position="none"), "Prevalence priors"),
  add_sub(p2 + theme(legend.position="none"), "Partial interpretations given fixed-thresholds"),
  add_sub(p3 + theme(legend.position="none"), "Full interpretations"),
  add_sub(p4, "Endorsement"),
           align = 'vh',
           labels = c("A", "B", "C", "D"),
           hjust = -1,
           nrow = 1,
           #rel_widths = c(1.2, 3, 2)
           rel_widths = c(1.2, 2.9, 1.15, 1.7)
           )
prow
```

```{r eval = F}
all.simulations.refactored <- all.simulations %>%
  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
  filter(Distribution != "Some", Distribution != "Most") %>%
  mutate(Distribution = factor(Distribution, levels = 
                                c( "Prior_generic", "Posterior_Generalization_generic"),
                                labels = c( "Prior/Silence", "Generalization")
                             # c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
                             #    labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")
                             ),
         PriorShape = factor(PriorShape, 
                             levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")
                            # levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
                             #labels = c("uniform", "bark","lay eggs","carry malaria","are female")
                                  #"eatsFood","areSick", "uniformRare", 
                                  #"carriesMalaria"
                                  )
         )

l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
                #lty = Distribution, 
                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
    geom_density(aes(y = ..scaled..),
                 size = 0.6,  adjust = 1.5)+
    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
    theme_few() +
    scale_color_solarized()+
    scale_fill_solarized()+
    scale_alpha_manual(values = c(0.7, 0.3))+
    scale_linetype_manual(values = c(1, 3))+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
   #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence of feature in a category") +
    ylab("Scaled probability density") +
  facet_wrap(~PriorShape, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0),
          legend.position = c(0.92, 0.35))

l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
    geom_density(aes(y = ..scaled..),
                 size = 0.6,  adjust = 1.5)+
    theme_few() +
    scale_color_solarized()+
    scale_fill_solarized()+
    scale_alpha_manual(values = c(0.7, 0.3))+
    scale_linetype_manual(values = c(1, 3))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence of feature in a category") +
    ylab("Scaled probability density") +
  facet_wrap(~PriorShape, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0),
          legend.position = c(0.92, 0.35))

```{r simulationsOld, eval = F, fig.cap = "Model behavior. Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions. The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 14, fig.height=6, cache=F}
grid.arrange(l0.simulations.distributions, 
             s1.simulations.scatter, ncol = 3,
             layout_matrix = cbind(c(1,1), c(1,1), c(2, 2)))

>>>>

```{r loadCachedSimulations, cache = F}
load("cached_results/modelSims-priors_fixedT_uncertainT_speaker.RData") # sims.priors, sims.fixed.thresholds, sims.uncertain.thresholds, s1.simulations.relabeled

s1.simulations.relabeled.2 <- left_join(
  s1.simulations.relabeled %>%  
    mutate(PriorShape = factor(example, 
                               levels = c("Dogs bark",
                                          "Kangaroos have spots",
                                          "Sharks don't eat people",
                                                      "Robins lay eggs",
                                                      "Robins are female",
                                                      "Mosquitos carry malaria"),
                               labels = c("bark", "have spots", "don't eat people", 
                                          "lay eggs", "are female", "carry malaria")),
              category = c("sharks", "robins", "robins", "kangaroos", "dogs", "mosquitos"),
              xlabpos = c(0.8, 0.5, 0.5, 0.325, 0.85, 0.325),
              ylabpos = c(0.12, 0.25, 0.25, 0.12, 0.12, 0.12)
           ),
                       data.frame(src =  c(rep("Prevalence priors", 6), rep("Interpretation posteriors",6 )),
                                  example = with(s1.simulations.relabeled, c(as.character(example), as.character(example))))
 ) %>%
   mutate(featureProb = ifelse(as.character(src) == "Prevalence priors", featureProb, -99),
          xlabpos = ifelse(as.character(src) == "Prevalence priors", xlabpos, -99))
```

```{r simulations, fig.cap = "Computational model simulations. Top: Prior distributions over the prevalence of a feature for 6 example features. Shapes of the priors were chosen to intuitively correspond to the properties labeling the distributions. Arrows show intuitive referent-category prevalence for a target category. Bottom: The interpreter model posterior distributions over prevalence upon hearing a generalization about a novel category. Numbers at bottom correspond to endorsement model predictions for endorsing the generalization for  the referent-category whose prevalence is shown in the top facets (e.g., \"Mosquitos carry malaria\").", fig.width = 9, fig.asp = 0.37, out.width = "100%", fig.align = "center", cache=F}

fig.sims.priors <- ggplot(
  bind_rows(sims.priors %>% 
              mutate(src = 'priors'),
            sims.uncertain.thresholds %>% 
              mutate(src = 'posteriors')
            ) %>% mutate(PriorShape = 
                           factor(PriorShape,  
                                  levels = c("barks", "hasSpots", "doesntEatPeople", "laysEggs", "isFemale", "carriesMalaria"),
                            labels = c("bark", "have spots", "don't eat people", "lay eggs", "are female", "carry malaria")),
                         src = factor(src, levels = c("priors", "posteriors"),
                                      labels = c("Prevalence priors", 
                                                 "Interpretation posteriors"))), 
  aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.7)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    # geom_rect(data = s1.simulations.relabeled.2,
    #           aes(xmin = featureProb - 0.05, xmax = featureProb + 0.05, ymin = 0.0, ymax = 0.15),
    #           fill = 'black', inherit.aes =F)+
    geom_segment(data = s1.simulations.relabeled.2,
              aes(x = featureProb, xend = featureProb, 
                  yend = 0.02, y = 0.2), size = 1,
              fill = 'black', inherit.aes =F, arrow = arrow(length = unit(0.2, "cm"),
                                                            type = 'open'))+
    geom_label(data = s1.simulations.relabeled.2,
                aes(x = xlabpos, y=0.25, label = category),
                label.padding = unit(0.075, "lines"),
                  family = 'Palatino', fontface = 'bold', size = 3.2, inherit.aes =F, force = 15)+
    ylab("Normalized probability density") +
    xlab("Prevalence")+
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(src~PriorShape, scales = 'free')+
    theme(strip.text.y = element_text(angle = 0, hjust =0),
          legend.position = "none", 
          plot.margin=unit(c(0.5,0.5,1.5,0.5),"cm"))

ggdraw(fig.sims.priors) + 
  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Dogs bark"),endorsement))[[1]], 2), 
             0.12, 0.12, fontface = "italic", fontfamily = "Times") +
  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Kangaroos have spots"),endorsement))[[1]], 2), 
             0.25, 0.12, fontface = "italic", fontfamily = "Times") +
  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Sharks don't eat people"),endorsement))[[1]], 2),
             0.36, 0.12, fontface = "italic", fontfamily = "Times") +
  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Robins lay eggs"),endorsement))[[1]], 2), 
             0.48, 0.12, fontface = "italic", fontfamily = "Times") +
  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Robins are female"),endorsement))[[1]], 2), 
             0.6, 0.12, fontface = "italic", fontfamily = "Times") +
  draw_label(round(unique(select(filter(s1.simulations.relabeled.2, example == "Mosquitos carry malaria"),endorsement))[[1]], 2), 
             0.72, 0.12, fontface = "italic", fontfamily = "Times") +
  draw_label("Endorsement Prediction", 0.885, 0.12, size = 10)
```
